\documentclass[12pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

\pagestyle{empty}

\begin{document}

\noindent
\today

\bigskip\bigskip

\noindent
Dear Editor,

\bigskip

\noindent
We are pleased to submit our manuscript entitled \textbf{``Post-Conflict Land Use Transitions in Urab\'a Antioque\~no, Colombia''} for consideration for publication in \textit{Ecological Economics}.

This study presents the first comprehensive multi-temporal land use and land cover change (LULCC) analysis of Urab\'a Antioque\~no in the post-conflict period (2013--2024). The region lies within the Choc\'o--Dari\'en biodiversity hotspot, one of the most biologically significant areas on Earth, yet remains critically understudied in terms of spatially explicit land use dynamics. Our work makes several contributions that we believe are well suited to the scope of this journal:

\begin{enumerate}
    \item We develop an 8-class Random Forest classification using Landsat and Sentinel-2 imagery in Google Earth Engine, including a dedicated mangrove class that enables blue carbon stock estimation---a first for this region at multi-temporal resolution.
    \item We employ Geographically Weighted Regression (GWR) to identify spatially heterogeneous drivers of deforestation, revealing how conflict legacies, infrastructure access, and coastal proximity interact across the landscape.
    \item We project land use to 2030 under three policy scenarios (business-as-usual, conservation with Kat\'{\i}os National Park buffer enforcement and mangrove restoration, and PDET-driven land restitution with sustainable agriculture) using a CA-Markov framework, quantifying trade-offs in carbon storage, habitat quality, and water yield.
    \item Our results enable direct cross-regional comparison with our companion study of Magdalena Medio, providing a paired analysis of two distinct post-conflict trajectories in Colombia.
\end{enumerate}

The findings are relevant to Sustainable Development Goals 6 (Clean Water), 13 (Climate Action), 14 (Life Below Water), 15 (Life on Land), and 16 (Peace, Justice and Strong Institutions).

This manuscript has not been published previously and is not under consideration elsewhere. All authors have approved the submitted version. We declare no conflicts of interest.

\bigskip

\noindent
Sincerely,

\bigskip\bigskip

\noindent
Cristian Espinal Maya (corresponding author)\\
School of Finance, Economics and Government\\
Universidad EAFIT, Medell\'{\i}n 050022, Colombia\\
\href{mailto:cespinalm@eafit.edu.co}{cespinalm@eafit.edu.co}

\medskip

\noindent
Santiago Jim\'enez Londo\~no\\
School of Applied Sciences and Engineering\\
Universidad EAFIT, Medell\'{\i}n 050022, Colombia

\end{document}
